Kyoto VR MQP Paper First Draft

### 2019-09-23 paper.tex
editour frontend testing section

\subsection{Frontend Web Application Testing}
\label{sec:frontendWebApplicationTesting}

>>>>

\subsection{Editour Frontend Testing}
\label{sec:editourFrontendTesting}

We suspect that Editour might have a life outside of this particular use case
for designing tours, depending on how we choose to further develop this
software. This is why Editour is perhaps more polished than your typical tool
purely for internal use.

For the duration of the project however, Editour only had to be used by us
three and Atticus. Therefore, the testing for the frontend of Editour was less
systematic than other parts of the software stack. This decision also helped us
focus our efforts on testing the reliability and user experience of ARuko. That
being said, we were able to add many feature and get the Editour experience to
a polished state through our own testing, using GitHub's tools to keep us
organized.

In order to test for bugs, all three of us periodically interacted with
successive builds of the frontend. When bugs were found, we would log these as
``Issues'' on the GitHub repo. These issues would get resolved in successive
pull requests.

Since we had to use Editour frequently to create test tours for ARuko, we were
able to identify features that would make our own work more efficient. This
worked as a kind of informal user testing. We kept track of feature requests
using the same system as bug reports.

Issues and feature requests alike got resolved in future pull requests. We
resolved over thirty issues and feature requests using this workflow. The
GitHub issues tab (which can be see in Figure~\ref{fig:issuesPageExample}) was
very useful for making sure we made use of our user testing and bug testing.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{issues-page-example.png}
	\caption{The GitHub issues tab for Editour}
	\label{fig:issuesPageExample}
\end{figure}
